\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx} % Professional Times typography
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{array}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{amssymb} % For checkboxes
\newcommand{\checkedbox}{\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{0.1em}$\checkmark$}}

% Custom Colors
\definecolor{headerblue}{RGB}{0, 51, 102}

% Header/Title Settings
\titleformat{\section}{\large\bfseries\color{headerblue}}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\large \textbf{CRUCIBLE TURBINE RATIFICATION SHEET}} \\
    \vspace{2mm}
    {\small \textbf{Group 05 | Project Orbit | PRID Framework}} \\
    \vspace{2mm}
    \textit{Document Status: PENDING RATIFICATION}
\end{center}

\vspace{5mm}

\section{Supervisory Directive}
This document records the official roles and duties for Project Orbit. As the Supervisor (PRID\_1), I am setting clear boundaries for each team member to ensure project security and organization. Every member must follow the rules listed below and stay within their assigned work area.

\section{Supervisory Designation (Reserved)}
The following role is fixed and held exclusively by the Project Architect.

\vspace{3mm}
\begin{spacing}{1.2}
\begin{tabular}{|l|l|p{8cm}|}
\hline
\textbf{ID} & \textbf{Assigned Member} & \textbf{Core Responsibilities} \\
\hline
\textbf{PRID\_1} & \textbf{Aditya Sadhu \checkmark} & \textbf{Supervisor:} Final project approval, security architecture, and merging all system modules. \\
\hline
\end{tabular}
\end{spacing}

\section{Consolidated Team Ratification}
The following roles are mandatory for the Project Orbit ecosystem. By ticking the box and signing your name, you acknowledge your assigned duties and agree to follow the security protocols.

\vspace{5mm}
\begin{spacing}{1.4}
\noindent \begin{tabular}{|l|l|p{5cm}|p{4.5cm}|c|}
\hline
\textbf{ID} & \textbf{Role} & \textbf{Key Responsibilities} & \textbf{Full Member Name} & \textbf{Tick} \\
\hline
PRID\_2 & \textbf{Auditor} & Tracking code precision, security audits, and log management. & Rohit Kumar Pandit & \checkedbox \\
\hline
PRID\_3 & \textbf{Designer} & Building UI layouts, static assets, and frontend cleanup. & Khushi Jamwal & \checkedbox \\
\hline
PRID\_4 & \textbf{Integrator} & Connecting modules, managing extensions, and fixing conflicts. & Vansita Rakwal & \checkedbox \\
\hline
PRID\_5 & \textbf{DBA} & Database schema design, data flow, and core/db security. & Shravan kumar & \checkedbox \\
\hline
\end{tabular}
\end{spacing}

\section{Security Protocol}
\begin{enumerate}
    \item \textbf{Work Zones}: Access is strictly restricted to your assigned PRID folder.
    \item \textbf{Access Rules}: Unauthorized file modifications will be automatically blocked.
    \item \textbf{Final Say}: PRID\_1 (Supervisor) holds exclusive authority for final merges.
\end{enumerate}

\vspace{10mm}

\section{Final Ratification \& Sign-off}
\vspace{5mm}

\begin{flushright}
\begin{spacing}{1.2}
    {\large \textbf{\textit{Aditya Sadhu \checkmark}}} \\
    \rule{6.5cm}{0.6pt} \\
    \textbf{Aditya Sadhu} (PRID\_1 Supervisor) \\
    \footnotesize \textit{Ratified on: \today}
\end{spacing}
\end{flushright}

\vspace{10mm}
\begin{center}
    \small \textit{This document is digitally locked under the Orbit Precision Guard 1.1.0 Protocol.}
\end{center}

\end{document}
